\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-09 ccs/pipe.tex
pass over paper. added partitioning figure.
forgot
para

We  now describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

@@

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, we first decompose the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the  decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program.
Resource analysis of high-level programs is a well-known hard problem~\cite{raml}
and we describe a heuristic analysis.

>>>>

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

@@

\noindent\textbf{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, we first decompose the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the  decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program.
Resource analysis of high-level programs is a well-known hard problem~\cite{raml}
and we describe a heuristic analysis.

### 2018-05-09 ccs/security.tex
para

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01} and provide provable security against all side-channel attacks.
At a very high level, in this
framework, parties are modeled as non-uniform interactive Turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.

>>>>

%\vspace{-0.2in}
\noindent\textbf{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01} and provide provable security against all side-channel attacks.
At a very high level, in this
framework, parties are modeled as non-uniform interactive Turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.
